\tool

### 2018-02-24 paper/paper.tex
Methodology updates and minor changes

\pseudosubsection{Patch Identification}

@@

\begin{itemize}
\item primariy written in Java,
\item ranked a top 1000 monthly forked repositoy in the last 10 years,
\item build using Maven, and
\item do not already utilize \textsc{Error Prone}.
\end{itemize}

We chose the most forked repositories to sample the most popular GitHub projects in terms of developer activity. Additionally, GitHub suggests forking repositories as a best practice for making contributions and pull requests to projects\footnote{https://guides.github.com/activities/forking/}. \textsc{Error Prone} only analyzes Java code, so this evaluation was limited to Java projects.  Maven is a build automation and dependency management system for Java projects. \tool~requires Maven to automatically modify \textit{pom.xml} files by adding the \textsc{Error Prone} plug-in and running the static analysis tool. Using a GitHub search API with the above constraints, we identified 2003 projects to use for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}}

>>>>

\pseudosubsection{Fix Identification}

@@

\begin{itemize}
\item primariy written in Java,
\item build using Maven,
\item do not already use \textsc{Error Prone},
\item have at least 100 stars,
\item ranked among the top forked repositories, and
\item have had 10 pull request opened in the last n days? %TODO: finalize project list
\end{itemize}

\textsc{Error Prone} only analyzes Java code, so this evaluation was limited to Java projects. Maven is a build automation and dependency management system for Java projects. \tool~requires Maven to automatically modify the \textit{pom.xml} files and run the tool. We chose the most forked and starred repositories to retrieve the most popular GitHub projects in terms of developer activity. GitHub suggests forking repositories as a best practice for making contributions and pull requests to projects\footnote{https://help.github.com/articles/fork-a-repo/}. Stars represent a social aspect of GitHub for users to indicate their favorite projects and repositories they are interested in\footnote{https://help.github.com/articles/about-stars/}. Using a GitHub search API, we identified 2003 projects to use for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}}
